\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{changepage}



% Ensure that generate pdf is machine readable/ATS parsable
\input{glyphtounicode}
\pdfgentounicode=1

\urlstyle{same}

\raggedbottom
\raggedright
% Adjust margins
\usepackage[letterpaper, margin=0.5in]{geometry}


% FONT OPTIONS
% \usepackage[lf]{venturis}

% \usepackage[default]{gfsbodoni}
% \usepackage[T1]{fontenc}

% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}
% make semi bold 
\renewcommand\bfdefault{sb}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


%-------------------------
% Sections formatting

%Main Sections
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[{\titlerule[0.5pt]} \vspace{0pt}]

% Resume Items
\newcommand{\resumeSingleItemBase}[1]{
\begin{adjustwidth}{0em}{0em}
    \vspace{-3pt}
    #1
\end{adjustwidth}
}

\newcommand{\resumeItemBase}[1]{\item
\resumeSingleItemBase{#1}
}

\newcommand{\resumeItem}[2]{\resumeItemBase{
    #1\hfill\small#2\\
}}

\newcommand{\resumeItemDetails}[4]{\resumeItemBase{
    #1\hfill\small#2\\
    #3\hfill#4\\
}}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=1em, label={}]}
\newcommand{\resumeItemListEnd}{\end{itemize}}


% Bullets
\newcommand{\resumeBullet}[1]{\item\small#1}

\newcommand{\resumeBulletListStart}{
    \vspace{-2pt}
    \begin{adjustwidth}{0em}{1em}
    \begin{itemize}[label=\tiny$\bullet$, leftmargin=1em]
}
\newcommand{\resumeBulletListEnd}{
    \end{itemize}
    \end{adjustwidth}
}



\begin{document}

\textbf{\LARGE Uzair Mohammed}\\
\vspace{2pt}
\href{mailto:moham147@msu.edu}{\underline{moham147@msu.edu}} {  }
\href{https://linkedin.com/in/uzair-m}{\underline{linkedin.com/in/uzair-m}} {  }
\href{https://github.com/uzairname}{\underline{github.com/uzairname}} {  }
\small 248-843-3985
\normalsize


\section{Education}

\resumeItemListStart
    \resumeItemDetails{\textbf{Michigan State University} - East Lansing, MI - Honors College, College of Engineering}{}{\textbf{B.S. in Computational Data Science}. Minor in Mathematics}{\textit{Grad: Apr. 2025}}
    \resumeItem{Relevant Coursework: \small Machine Learning, Deep Learning, Data Analysis \& Visualization, Software Engineering, Data Structures \& Algorithms, Database Systems, Scientific Programming, Linear Algebra, Differential Equations, Physics, Economics, Linguistics.}{}

\resumeItemListEnd

\section{Experience}

\resumeItemListStart

    \resumeItem
        {\textbf{Workshop Director} - MSU Artificial Intelligence Club}{\small{\textit{Sep. 2022 -- Present}}}
        
        \resumeBulletListStart

            \resumeBullet{Lead a team of organizers to plan and execute weekly meetings at MSU's premier computer science student organization.}
            \resumeBullet{Provide over 1000 students with hands-on learning in in computer vision, natural language processing, and generative AI using Scikit-Learn, PyTorch, OpenCV, and other technologies. Doubled member engagement over 3 semesters.}
            \resumeBullet{Establish timelines, assess content quality, develop connections, and implement feedback from advisors and students.} %kaggle, google colab, opencv, LangChain, Hugging Face, Kaggle, OpenCV, Streamlit
            
        \resumeBulletListEnd


    \resumeItem
      {\textbf{AI Engineer} - Youlearn.ai}
      {\textit{Sep. 2023 - present}}
    \resumeBulletListStart
      \resumeBullet{Lead a team of 6 to develop a personalized, NLP-driven education service using agile practices, reaching >1000 users.}
      \resumeBullet{Deployed a vector store and retrieval augmented generation to create an AI tutor based on scraped online content.}
    \resumeBulletListEnd
    
    
    \resumeItem{\textbf{Mathematics Researcher} - University Undergraduate Research and Arts Forum}{\textit{\small{Apr. 2022}}}
    
        \resumeBulletListStart
        
            \resumeBullet{Analyzed properties of a novel combinatorial game using alpha-beta pruning, and benchmarked complexity against similar games, using SciPy and SageMath. Presented findings and published a video at UURAF to >100 researchers and students.}
            
        \resumeBulletListEnd
    

\resumeItemListEnd

\section{Projects \& Awards}

\resumeItemListStart

    \resumeItem
      {\textbf{Awarded Second Place} - Terminal AI - MHacks 16}
      {\textit{Nov. 2023}}
      \resumeBulletListStart
        \resumeBullet{Collaborated with a team of 4 to develop a Python library and CLI that captures errors, analyzes a codebase, and gives intelligent suggestions in the terminal using GPT. Awarded "best developer tool" in the MHacks 2023 hackathon}
      \resumeBulletListEnd

    \resumeItem
      {\href{https://www.spaceappschallenge.org/2023/find-a-team/hatchlings/?tab=project}{\textbf{Awarded Global Nominee} - Open Source Marketplace - NASA Space Apps Challenge}}{\textit{Oct. 2023}}
      \resumeBulletListStart
        \resumeBullet{Developed an app with a team of 5 to network contributors and open science repositories based on skills and interests.}
        \resumeBullet{Trained a recommendation algorithm with link prediction and OpenAI embeddings to connect hundreds of users and repos.}
      \resumeBulletListEnd


    \resumeItem
      {\href{https://devpost.com/software/hologlass}{\textbf{Awarded Best Use of AI} - Live Transcription Glasses - HackUIowa 2023}}{\textit{Sep. 2023}}
      
        \resumeBulletListStart
        
            \resumeBullet{Developed the back-end of a full stack speech recognition device with a 4-person team to improve accessibility.}
            
            \resumeBullet{Integrated Cohere and Google Cloud Speech to Text APIs to display and summarize live conversations to one's field of view.}
            
        \resumeBulletListEnd

    \resumeItem
      {\href{https://hack-dearborn-2023.ctfd.io/users/27}{\textbf{Awarded First Place} - CTF Cybersecurity Challenge - Hack Dearborn 2}}{\textit{Oct. 2023}}

    \resumeItem{\textbf{MSU Quantitative Finance Club} - Member}{\textit{Sep. 2023 - present}}
    
        \resumeBulletListStart
        
            \resumeBullet{Actively engage in weekly meetings to learn about quant development and research from industry professionals.}
            
        \resumeBulletListEnd

    \resumeItem
        {\textbf{AI Resume Matcher} - NLP Project}
        {\textit{Jan. 2023}}
        
        \resumeBulletListStart
        
            \resumeBullet{Designed a semantic search pipeline to match resumes to job postings using spaCy and the Cohere API. Analyzed over 50 skills. Prototyped a Flask web app with a team of 4 for the SpartaHack 8 Hackathon.}
            
        \resumeBulletListEnd


        % YouLearn - Lead Developer




    \resumeItem
        {\href{https://www.msuaiclub.com/projects/smart-attendance}{\textbf{Smart Attendance} - Computer Vision Project}}
        {\textit{Sep. 2021 - Jan. 2022}}
        
        \resumeBulletListStart
        
            \resumeBullet{Developed a web app with a team of 12 to automate taking attendance with a camera.}
            
            \resumeBullet{Applied a convolutional neural network in Dlib to recognize and compare faces, achieving 99.4\% accuracy.}
            
            % \resumeBullet{Collaborated with a team of 6, implementing best practices for Python code documentation and version control in git.}
            
        \resumeBulletListEnd


    \resumeItem
        {\textbf{Statistical Skill Ranking \& Matchmaking} - Full Stack Application}
        {\textit{Jan. 2021 - Dec. 2022}}
        
        \resumeBulletListStart
        
            \resumeBullet{Invented a Bayesian Elo model to match players and manage leaderboards for competitive games, serving \textbf{200 users}.} 
            
            \resumeBullet{Configured a CI/CD pipeline with GitHub Actions and Docker to deploy an app to AWS EC2, reducing build time and errors.}
            
        \resumeBulletListEnd


\resumeItemListEnd



\section{Technical Skills}

\resumeItemListStart

    \resumeItem{\textbf{Languages \& Technologies: }\small Java, Python (PyTorch, Scikit-Learn, spaCy, Pandas), C++, R, Typescript, JavaScript, MATLAB, Git, SQL (Postgres, SQLite), GraphQL, Vector databases, Hugging Face, MongoDB, Docker, AWS, Azure, Google Cloud Platform, Maple, SageMath.\normalsize}{}

\resumeItemListEnd



\section{Honors}

\resumeSingleItemBase{


    \begin{center}
        Dean's List (2021-2023)\hfill National Merit Semifinalist (2021)\hfill MSU Special Merit Scholarship (2021)\hfill Eagle Scout (2018)
    \end{center}
}


    
\end{document}
